### 2018-04-02 Sections/economics_of_the_quantum_internet.tex
Minor economics

@@

\begin{figure}[!htb]
	\includegraphics[width=0.4\textwidth]{network_value}
	\caption{Dollar value (in units of \mbox{$C_0N_0$}) of the network as a function of time, growth rate in the number of physical qubits, and rate of decay in the dollar value of physical qubits. When \mbox{$\gamma_N/\gamma_C=1$} the network's value remains constant over time. Above this the network's value appreciates exponentially, and below this it depreciates exponentially against time.} \label{fig:network_value}
\end{figure}

>>>>

%
% Network Power
%

\subsection{Network power}

First and foremost, with a fully interconnected quantum computational network, what is the projection of its net computational power now and into the future? This is simply obtained via the joint computational scaling function applied to projected network size,

\begin{postulate}[Network power]\label{post:network_power}\index{Network power}
The combined computational power of the entire network, measured in FLOPS, is given by,
\begin{align}
n_\text{FLOPS}(t) &= f_\text{sc}(n_\text{global})\nonumber \\
&= f_\text{sc}(N_0{\gamma_N}^t).
\end{align}
\end{postulate}

@@

\begin{figure}[!htb]
	\includegraphics[width=0.4\textwidth]{network_value}
	\caption{Dollar value (in units of \mbox{$C_0N_0$}) of the network as a function of time, growth rate in the number of physical qubits, and rate of decay in the dollar value of physical qubits. When \mbox{$\gamma_N/\gamma_C=1$} the network's value remains constant over time. Above this the network's value appreciates exponentially, and below which it depreciates exponentially against time.} \label{fig:network_value}
\end{figure}
